RNA-seq from 4 cell populations

### 2021-11-01 deconvolution/fans4/molec_profiling.Rmd
per cell type
add per cell type analysis

@@

```{r excludeIDs}
excludeIDs = c('CMC_MSSM_002')
info = info[! info$Individual.ID %in% excludeIDs,]
```

@@

# Per cell type analysus
```{r preprocess}

for( CT in unique(info$CellType) ){

@@

  dge = DGEList( geneCounts[isexpr,] )
  dge = calcNormFactors(dge)

  form = ~ (1|Gender) + (1|Batch)
  vobj = voomWithDreamWeights(dge, form, info, plot=TRUE, save.plot=TRUE, BPPARAM=SnowParam(12, progressbar=TRUE))

  form = ~ (1|Gender) + (1|Batch) ~ Batch + Gender + Age.of.Death
  fit = dream(vobj, form, info, BPPARAM=SnowParam(12, progressbar=TRUE)))

# contrasts
# L = makeContrastsDream(form, info, contrasts=c(
#               GABA.Dx = "IGABA.SCZ - IGABA.Control",
#               GLU.Dx = "IGLU.SCZ - IGLU.Control",
#               MgAs.Dx = "IMgAs.SCZ - IMgAs.Control",
#               Olig.Dx = "IOlig.SCZ - IOlig.Control"))

}

>>>>

```{r}
CODE <- Folder(name = "results", parentId = "syn26433312")
CODE <- synStore(CODE)

# Store data 
storeData = function( obj, file, description){
  saveRDS( obj, file=file)

  nEXP_OBJ = File(file, 
                  name = description, 
                  parentId = CODE$properties$id)
  synStore(nEXP_OBJ, used = ALL_USED_IDs, executed = thisFile)
}
```

@@

```{r excludeIDs}
excludeIDs = c('CMC_MSSM_002')

incl = !colnames(geneCounts) %in% rownames(info[info$Individual.ID %in% excludeIDs,])
geneCounts = geneCounts[,incl]
info = info[! info$Individual.ID %in% excludeIDs,]

identical(rownames(info), colnames(geneCounts))
```

@@

### Save processed data
```{r save.processed}
storeData( geneCounts, "geneCounts_merged.RDS", "Merged gene counts for Mol Prof data")
storeData( info, "info_merged.RDS", "Merge metadata for Mol Prof data")
```

# Per cell type analysus
```{r preprocess.CT}
ALL_USED_IDs= unique(c('syn22321012', 'syn22321013', 'syn22321014', 'syn22321016', 'syn2232101', 'syn26000845','syn25976117', 'syn25976127', 'syn22321013', 'syn22321014', 'syn22321016', 'syn26000850', 'syn25976122', 'syn25976136'))

resByCT = lapply(unique(info$CellType), function(CT){

@@

  form = ~ (1|Gender) + (1|Batch)
  vobj = voomWithDreamWeights(dge, form, info[idx,], plot=TRUE, save.plot=TRUE, BPPARAM=SnowParam(12, progressbar=TRUE))

  form = ~ Dx + (1|Gender) + (1|Batch) + Batch + Gender + Age.of.Death
  fit = dream(vobj, form, info[idx,], BPPARAM=SnowParam(12, progressbar=TRUE))
  fit = eBayes(fit)

  resDE = topTable(fit, coef="DxSCZ", number=Inf)
  resids = residuals(fit)

  # save results for this cell type
  storeData( vobj, paste0("voomObj_", CT, ".RDS"), paste0("voom fit for ", CT))
  storeData( fit, paste0("fit_Dx_", CT, ".RDS"), paste0("dream fit for ", CT))
  storeData( resDE, paste0("de_Dx_", CT, ".RDS"), paste0("Differential expression within ", CT))
  storeData( resids, paste0("residuals_", CT, ".RDS"), paste0("Residuals for ", CT))
})
```
